### 2022-02-23 sections/strategy_Htautau.tex
add new limit plots

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and not reconstructed.
This kind of events will fall into $t_hH$.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and H can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the tau-leptons 
are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is assumed to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
%has a large momentum and the flying direction is unknown.
the kinematics fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
in Section~\ref{sec:tmva}.

@@

   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule

@@

 \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
 \text{Min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\

@@

 $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
 $\Delta R(\tau1,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
 $\Delta R(\ell+\text{b-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\

@@

 \text{Min}($m_{\text{light-jet},\text{light-jet}}$) &   &  $12$               &           & $11$     &       &  &         \\

@@

A large set of potential variables are investigated in each SR separately. The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.

@@

\item \text{Min}($M_{\tau\tau \text{q-jet}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
\item \text{Min}($M_{\text{light-jet},\text{light-jet}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

@@

%\item \text{Max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.

@@

The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model} below.

@@

The final observable used to extract signal events is defined as the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.
%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

>>>>

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
This kind of events will fall into $t_hH$.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
In the $t_hH$ events, there are three jets coming from top hadronic decay including the $b$-jet and two opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

For the  $t_lt(qH)$ and $t_lH$ events where the $W$ boson from $t\to W b$ decay decays leptonically,
%has a large momentum and the flying direction is unknown.
the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
in Section~\ref{sec:tmva}.

@@

   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l2\tauhad$     & $t_h2\tauhad$-2j & $t_h2\tauhad$-3j       \\\midrule

@@

 \text{min}($m_{\tau\tau j/g}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
 \text{min}($\Delta R(\ell,\tau)$)                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\

@@

 $\Delta R(\ell,\text{$b$-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
 $\Delta R(\tau1,\text{$b$-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
 $\Delta R(\ell+\text{$b$-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\

@@

 \text{min}($m_{jj}$) &   &  $12$               &           & $11$     &       &  &         \\

@@

A large set of potential variables are investigated in each SR separately. The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of the events) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is larger than 2\% were kept.

@@

\item \text{min}($m_{\tau\tau j/q}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\text{t},\text{FCNC},\text{vis}}$.
\item \text{min}($m_{jj}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

@@

%\item \text{max}($\eta_{\tau}$) is the maximum $\eta$ value among the tau candidates.

@@

The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.

@@

The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

### 2022-02-23 sections/systematic_uncertainties.tex
add new limit plots

Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated approximately 30\% by comparing the
data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-jet.
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.

>>>>

Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by comparing the
data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-jet.
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.
